Simulations log

### 2020-04-24 manuscript/drafts/manuscript.Rmd
Upgrade hyperparameter optimization plots \n add bar plots for discrete hyperparameters
- update introduction section,

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output:
  word_document: default
  pdf_document:
    citation_package: biblatex
bibliography: asreview.bib
---

@@

#### Introduction 
#### Methods
A convenience sample of 5 existing systematic reviews on varying topics was collected.

@@

\newpage
# Introduction
Systematic Reviews (SR's) are booming - but they are a lot of work
Various machine learning tools have been proposed to reduce workload in abstract screening.

- objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
- justification - 
- background 
- guidance to reader 
- summary/conclusion

@@

This study is about how machine learning algorithms can increase efficiency in systematic reviews. I will write about what SRs are, and how workload can be reduced.

Systematic reviews are top of the bill in research. As more and more papers are published and reproducibility crisis has emerged, science calls for more meta. It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […]. Performing a systematic review is a tedious and time-consuming task. To review a specific research area, one starts out with an initial search of thousands of academic papers. All these papers abstracts need to be screened to find an initial batch of possibly relevant papers. With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?].  This whole processes costs this and this much time [shelmilt].

@@

So you might wonder, how does such an algorithm actually work? Active learning strategy, starting with a pool of unlabeled abstracts (U). The reviewer starts labeling some instances in U, creating L. The algorithm utilizes L to predict labels for all abstracts (classifier), by using a set of features from the papers called X, for example the text in the abstract (feature extraction method). Now, it made an initial classification. The algorithm now aims to improve its classification by which paper from U will be presented to the reviewer next. By labeling the next paper, the reviewer provides the algorithm with new information which the algorithm uses to update its prediction.

@@

  M = train($\mathcal{L}$)
  Query x \isin \mathcal{U} (<x, y=?)
  oracle <x, y>

@@

In the current study, we aim at exploring the performance of several classifiers on reducing workload while maintaining performance in abstract screening process. This is done by performing simulations on existing systematic reviews. Performance is evaluated by how much time can be saved … while maintaining accuracy.

Present research questions. 
RQ1 – which classifiers perform best? 
-	RQ1a – does classifier performance vary over different research areas? 
(in what terms does it perform best)

RQ2 different hyperparameter optimizations?
Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.

@@

This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.

All simulations were run using through cartesius EINF-156 
Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
What would happen if the citation screening would have been performed using asreview? 
All datasets accompanying the systematic reviews are openly published. 
We built several machine learning models to perform automated systematic reviews, 
who are then applied on existing systematic reviews.

\newpage
# Methods
Performance of several machine learning models was demonstrated on six systematic review datasets.

@@

>>>>

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "22/04/2020"
output:
  pdf_document:
    citation_package: biblatex
#  word_document: default
bibliography: asreview.bib
---

@@

Keywords: Human-Machine interaction, active learning, systematic reviews, text classification

#### Introduction 
<!-- This study aims to contribute to this growing area of research by exploring  -->

#### Methods
<!-- A convenience sample of 5 existing systematic reviews on varying topics was collected. -->

@@

\newpage
# Introduction
Systematic reviews are top of the bill in building evidence in research. A systematic review attempts to bring together all studies relevant to answer a specific research question [@PRISMA-PGroup2015]. Systematic reviews inform practice and policy [@Gough2002] and are key in developing clinical guidelines [@Chalmers2007]. 
<!-- PRISMA definition:  -->
<!-- > "A systematic review attempts to collate all relevant evidences that fits pre-specified eligibility criteria to answer a specific research -->
<!-- question.

add that htis is a systematic/rigorous process?-->

Systematic reviews are costly. Conducting a systematic review involves the manual screening of thousands of titles and abstracts, identifying publications relevant to asnwering the research question. This process typically requires over a year of work from a team of researchers [@Borah2017]. Besides time-consuming, the process of title and abstract screening is also prone to human error [@Wang2020].
<!-- (14 to 77,910, trimmed mean 1,286).  -->
<!-- Need to be screened by multiple researchers.  -->

<!-- As the number of scientific publications is growing at an increasing rate [source], the workload in SR is getting heavier.  -->

As time and resources are limited, it is often impossible to meet the strict criteria of a systematic review. 
Currently, the demand for systematic reviews exceeds the available capacity by far [@Lau2019].
Moreover, the required resources for a systematic review is making it difficult to timely respond to urgent matters.
An example of this is the need for clinical guidelines in the current covid-19 crisis. 
To ensure a timely review, reducing workload in systematic reviews is imperative.

With advances in Artificial Intelligence (AI), a plethora of methods have been proposed to reduce workload in systematic reviews [@Harrison2020]. More specifically, the field of AI-aided title and abstract screening is rapidly evolving [@OMara-Eves2015].
Machine Learning (ML) models have been proposed, aiming to assist the reviewer by detecting whether a given publication is relevant or irrelevant to the systematic review. Findings suggest such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications (95% recall) [@OMara-Eves2015].
Screening prioritization is a well-established approach in increasing efficiency in title and abstract screening [@Yu2018] [moresources].
The publications to be screened are ordered by their likeliness of relevance, seeing all relevant publicatoins much earlier on in the screening process when they would have been read in a random order.

Screening prioritization reorders   
Their objective is to assist the reviewer in the screening process by prioritizing publications most likely to be relevant.

recent research/promising Active Learning.

The current study focus is on reducing workload by prioritizing the most relevant abstracts. Presenting the abstracts orders the abstracts by likelihood of relevance, e.g. th The reviewer sees the most relevant abstracts first, If the model performs well all relevent abstracts will be seen much earlier than when abstracts are read at a random order.

The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions. It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.

In most recent studies, 
The latest state-of-the-art methods implement active learning, where the model improves its prediction of relevance based on the reviewers latest decisions in the screening process [@Yu2018; @Miwa2014]. 
The ML-model, where the ML-model orders the most

In most recent studies, X has been measured in four different ways.
The use of qualitative case studies is a well-established approach in …

Their objective is

"Screening is performed in two steps, first preliminarily based on title and abstract,
then based on full-text." 
Screening a title + abstracts takes 30 seconds on average, for an experienced reviewer, and longer for inexperienced ones [@Wallace2010].

<!-- add: current consensus active learning are state of the art: how do they woroK; by prioritizatio (put in a picture)  -->

<!-- #### identifying the niche  -->
Although considerable research has been devoted to the effectiveness of ML-models in reducing workload in title and abstract screening, the complex nature of the field makes it difficult to draw overarching conclusions about best practice [@OMara-Eves2015]. The lack of replication on data outside the biomedical sciences makes it impossible to draw conclusions about the general effectiveness of such technologies [@OMara-Eves2015]. 
Taken together, these issues prohibit the adoptation of AI-aided title and abstract screening by systematic reviewers.

[@Marshall2020]

<!-- By evaluating different configurations of an active learning model on different review contexts.  -->
<!-- status quo: prioritization + active learning? + certainty [@Miwa2014], but classifier  -->
<!-- Although several studies attempt to evaluate such methods,  -->
<!-- It makes  -->
<!-- although  tackle issues in the (complex) area,  -->
<!-- Furthermore, few studies have investigated the use of different classifiers in any systematic way -->
<!-- AI-aided title and abstract screening has been proven succesful in reducing workload, but a lack of replication and  -->

<!-- Furthermore, a comparison mode in public health and clinicial medicing [@Miwa2014] compared different classifier on different datasets and found differential performance on 'messier' social sciences datasets.   -->

<!-- #### Occupying -->
<!-- ##### (listing purpose of new research,  -->
The current study aims to address these concerns in the following ways:

1) Combining latest insights from the field of AI-aided title and abstract screening, various ML-models for screening prioritization are built.
2) To evaluate model performance across different review contexts, the models are simulated on multiple datasets from various research areas, of which the data is openly accessible.
3) To ensure replication and transparency, the simulations are implemented in an open source pipeline called `ASReview`. 
<!-- The tool is generic such that any researcher can adjust modules to increase efficiency in this field.   -->

This study set out to increase the evidence base of ML-models aiming to reduce workload in title and abstract screening in systematic reviews. Working towards a general consensus in this emerging field, performance of state-of-the art ML-models is evaluated over various research contexts. To further increase usability and acceptability of such models amongst systematic reviewers, the study presents a reproducible workflow.

 <!-- [@OConnor2019] -->

<!-- ##### listing questions,  -->
<!-- This study .  -->
<!-- research questions:  -->
<!-- RQ1 – how -->
<!-- -	RQ1a – does classifier performance vary over different research areas? -->
<!-- (in what terms does it perform best)  -->

<!-- ASReview aims to reduce workload in the citation screening process by prioritizing the most relevant abstracts.  -->
<!-- ASReview combines in text classification  -->

<!-- Furthermore, this study makes a contribution to ...  by demonstrating a reproducible and flexible tool,  -->
<!-- Furthermore, a generic and reproducible workflow is presented to facilitate, hopefully to increase acceptability and usability by researchers performing systematic reviews.  -->

The remaining part of this paper is organized as follows: first, a short review of state-of-the art methods is given. Second, the proposed ML-models will be explained on a conceptual level. Third, the methods section gives a detailed description of the study design. The results section ... and last, the results will be discussed.

@@

Active learning is the approach where   [@Settles2002]

Study selection in systematic review process

#### summarise models used
#### propose pipeline 
##### and specific components?

#### summarise datasets tested
\
\

Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
What would happen if the citation screening would have been performed using asreview? 
All datasets accompanying the systematic reviews are openly published. 
We built several machine learning models to perform automated systematic reviews, 
who are then applied on existing systematic reviews.

Openness, reproducible,

Benefits:

Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies. 
meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.

paper organization:

Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers. 
Few studies have evaluated different classifiers in any systematic way
different models to use haven't been investigated in a systematic way (only in software engineering)

1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening. 
2) screening prioritization is appealing to systematic reviewers because ...
3) 
4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.

lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?)
There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering

However, there is a need for consensus () and transparancy?

So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.

Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).

##### indicating the structure of the writing)
principle findings:

<!-- RQ2 different hyperparameter optimizations? -->
<!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->

For truly evaluate the effectiveness of such methods,

automatically (by machine learning techniques)
In the current study we focus on the effectiveness of different machine learning models in reducing workload in the citation screening process. 
Assisting the reviewer. Combining various machine learning techniques. 
Combining recent insights on, we propose ASReview.
Approaching the citation screening phase as a classfication task,
The benefit is that ASReview is dynamic, user can decide
open source, multiple classifiers and other settings,

The current study focus is on reducing workload by prioritizing the most relevant abstracts. Presenting the abstracts orders the abstracts by likelihood of relevance, e.g. th
The reviewer sees the most relevant abstracts first, 
If the model performs well all relevent abstracts will be seen much earlier than when abstracts are read at a random order.

Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..

#### Proposed solution
This study is about how machine learning models can increase efficiency in systematic reviews.
Their main objective is to identify ..

The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review. 
As the relevant publications are screened first, the reviewing process can be quit earlier.

@@

### Background
... starts with a search for potentially relevant publications. 
This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question. 
Because the initial set often consists of thousands of papers and the

To gather the findings relevant to answering the research question, a systematic search is performed.
A systematic search starts with collecting all publications that meet pre-specified eligibility criteria.
From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question. 
Of all candidate studies only a fraction is relevant [...].

As more and more papers are published and reproducibility crisis has emerged, 
A systematic search often results in thousands of candidate studies.
Relevant publications are then identified by screening title and abstract of all candidate studies. 
This screening process is a manual task often executed by multiple reviewers to ensure reliability. 
This is a time consuming process that weighs heavily on resources.

A solution is ...

It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].

To review a specific research area, one starts out with an initial search of thousands of academic papers. All these papers abstracts need to be screened to find an initial batch of possibly relevant papers. With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?]. This whole processes costs this and this much time [shelmilt].

#### Technical details
So you might wonder, how does such an algorithm actually work? Active learning strategy, starting with a pool of unlabeled abstracts (U). The reviewer starts labeling some instances in U, creating L. The algorithm utilizes L to predict labels for all abstracts (classifier), by using a set of features from the papers called X, for example the text in the abstract (feature extraction method). Now, it made an initial classification. The algorithm now aims to improve its classification by which paper from U will be presented to the reviewer next. By labeling the next paper, the reviewer provides the algorithm with new information which the algorithm uses to update its prediction.

@@

  M = train($\mathcal{L}$)
  Query x isin mathcal{U} (<x, y=?)
  oracle <x, y>

@@

@@

\newpage
# Methods
This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.

All simulations were run using through cartesius EINF-156

Performance of several machine learning models was demonstrated on six systematic review datasets.  
study design: retrospective

@@

- we look for final inclusions but we screen only the abstracts (do they satisfy the imformation need  (blake (page 19 omara et evs)))

future research: 
- stopping rule is not discussed
- computation/retraining time

strengths:

- open data
- different research areas
- different models on same dataset
- different datasets on same model

limitations

future research
- all models save time, difficult to distinguish performance over datasets, especially when applied on a dataset of which no prior information is known (e.g. inclusions isn't known in practice). Perhaps go for other criteria like the fastest model, replicate study with computation time?

Simulating the title and abstract screening process, models are evaluted on their capability/speed of detecting the final inclusions. 
However, in a manual SR these final inclusions are selected after reading the fulltext. Information the text mining tool does not have. 
To truly assess the added value of such a tool, models should be evaluated on their capability of detecting the abstract inclusions. 
Call for systematic reviewers to openly publish need for open data containing abstract inclusions, not only final inclusions!

### 2020-04-24 simulation_study/hpoptimization/README.Rmd
- update introduction section,

php_c <- function(data){
  data %>%
    filter(param %in% categoricalvars) %>%
    mutate(value = as.factor(value)) %>% 
    ggplot(aes(x = value, color = group, fill = group, group = group)) +
    geom_bar(position="dodge") +
    facet_wrap(vars(param), nrow = 2, scales = "free_x") +
    labs(title = "(optimal) categorical hyperparameters", y = "", x = "Parameter values")+
    theme_minimal()
}
```

@@

@@

## Loss plots
Two times the same data, first plot is over trials, second sorted from highest to lowest loss.
```{r}
nbtfidftrials <- readRDS("trials/nb_tfidf-trials.RDS")

@@

Inspect outliers: 
```{r}
# inspect outliers
hpsets$nb_tfidf %>% filter(param %in% c("balance_param.a", "model_param.alpha")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb)
```

@@

@@

Inspect outliers
```{r}
hpsets$lr_tfidf %>% filter(param %in% c("balance_param.a", "model_param.c")) %>% group_by(param) %>% filter(value > 40) %>% select(-ub, -lb)
hpsets$lr_tfidf %>% filter(param %in% c("model_param.class_weight")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb)
```

>>>>

php_c <- function(data){
  data %>%
    filter(param %in% categoricalvars) %>%
    mutate(value = as.factor(value)) %>% 
    ggplot(aes(x = value, color = group, fill = group, group = group)) +
    geom_bar(position="stack") +
    facet_wrap(vars(param), nrow = 2, scales = "free_x") +
    labs(title = "(optimal) categorical hyperparameters", y = "", x = "Parameter values")+
    theme_minimal()
}
```

@@

## Results
Loss plots: Two times the same data, first plot is over trials, second sorted from highest to lowest loss.

Hyperparameters on a continuous scale are plotted as dots in a scatterplot. 
Discrete hyperparameters are displayed in a barplot

Conclusions: 
- loss is going down over trials 
- some datasets go down faster
- some datasets go down more

@@

## Loss plots

```{r}
nbtfidftrials <- readRDS("trials/nb_tfidf-trials.RDS")

@@

Inspect outliers: 
```{r}
# inspect outliers
hpsets$nb_tfidf %>% filter(param %in% c("balance_param.a", "model_param.alpha")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb) %>%
  kable(format = "markdown")
```

@@

hpsets$svm_tfidf %>%
  php_c() 
```
# SVM + Doc2Vec

```{r SVM_D2V}
svmd2vtrials <- readRDS("trials/svm_d2v-trials.RDS")

svmd2vtrials <- svmd2vtrials %>%
  group_by(datasets) %>%
  mutate(index = rev(index))

# loss plot by index 
svmd2vtrials %>% 
  loss_i()

# loss plot sorted by trial numbers 
svmd2vtrials %>%
  loss_t()

@@

Inspect outliers
```{r}
hpsets$lr_tfidf %>% filter(param %in% c("balance_param.a", "model_param.c")) %>% group_by(param) %>% filter(value > 40) %>% select(-ub, -lb) %>%
  kable(format = "markdown")
hpsets$lr_tfidf %>% filter(param %in% c("model_param.class_weight")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb) %>%
  kable(format = "markdown")
```

### 2020-04-24 simulation_study/simulation/README.Rmd
- update introduction section,

createLines <- function(cond, d, hp){
  comm <- "./cart_simulate.py simdata/%s.csv --config_file simconfig/%s/%s/%s-%s.ini --state_file simoutput/%s/%s/%s/results.h5 -r 15"
  files <- data.frame(c = condition, 
                    f = c("nb_max_double_tfidf",
                    "rf_max_double_tfidf",
                    "svm_max_double_tfidf",
                    "logistic_max_double_tfidf",
                    "nn-2-layer_max_double_tfidf",
                    "nb_max_double_doc2vec",
                    "rf_max_double_doc2vec",
                    "svm_max_double_doc2vec",
                    "logistic_max_double_doc2vec",
                    "nn-2-layer_max_double_doc2vec"))

@@

  # write 
  script <- sprintf(comm, 
        # input data
        cons$d, 
        # config file details
        cons$hp, cons$c, cons$f, cons$d,
        # output file details
        cons$hp, cons$c, cons$d)
return(script)
}
transfer <- function(hp, c){
    cons <- expand.grid(hp = hp, c = c, stringsAsFactors = FALSE)
    txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s/%s"

    sprintf(txt, hp, c, hp, c)
}

@@

@@

```{r}
# LCTD and SCDD both failedsimulations both failed? 
# ran again 
# transfer to harddrive
transfer("one", condition[c(4,7:9)])
# sctd is not finished yet! 
sims[condition[4],,"one"] <- 3 # output is on harddrive

@@

sims[condition[9],,"one"] <- 3 # output is on harddrive 
# but ace wasn't finished yet!

@@

```{r}
# run again 
# transfer to harddrive 
transfer("one", condition[8])

#sims[condition[8], , "one"] <- 3 # output is on harddrive
```

### all 
```{r}
# manually transform
# push to github 
sims[condition[4], , "all"] <- 1 # configs are on github

```{r}
# run simulations 
# lctd_n <- createLines(condition[4], d, "all")
# write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
#             row.names = FALSE)
# names(lctd_n) <- c()
# #sims[condition[4], d, "all"] <- 2 # simulations are running 
# 
# # transfer to harddrive 
# transfer("n", condition[4])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```

>>>>

createLines <- function(cond, d, hp, seed = FALSE){
  comm <- "./cart_simulate.py simdata/%s.csv --config_file simconfig/%s/%s/%s-%s.ini --state_file simoutput/%s/%s/%s/results.h5 -r 15"
  files <- data.frame(c = condition, 
                    f = c("nb_max_double_tfidf",
                    "rf_max_double_tfidf",
                    "svm_max_double_tfidf",
                    "logistic_max_double_tfidf",
                    "nn-2-layer_max_double_tfidf",
                    "nb_max_double_doc2vec",
                    "rf_max_double_doc2vec",
                    "svm_max_double_doc2vec",
                    "logistic_max_double_doc2vec",
                    "nn-2-layer_max_double_doc2vec"))

@@

  # write 
  script <- sprintf(comm, 
        # input data
        cons$d, 
        # config file details
        cons$hp, cons$c, cons$f, cons$d,
        # output file details
        cons$hp, cons$c, cons$d)

  if(seed){
    script <- paste0(script, " --init_seed 42")
  }
return(script)
}
transfer <- function(hp, c, seed = FALSE){
    cons <- expand.grid(hp = hp, c = c, stringsAsFactors = FALSE)

    if(seed){
      txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s_seed/%s"
    } else {
      txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s/%s"
    }
    result <- sprintf(txt, hp, c, hp, c)
    return(result)
}

@@

ASReview version 0.8.1

@@

```{r}
# LCTD and SCDD both failedsimulations both failed? 
# ran again 
# transfer to harddrive
transfer("one", condition[c(4,7:9)])

# sctd is not finished yet! 
sims[condition[4],,"one"] <- 3 # output is on harddrive

@@

sims[condition[9],,"one"] <- 3 # output is on harddrive 
# but ace wasn't finished yet! 
```

```{r}
# run again 
# transfer to harddrive 
transfer("one", condition[8])
```

15.04.2020 
```{r}
transfer("one", condition[3]) # SCTD 
sims[condition[8], , "one"] <- 3 # output is on harddrive

# BCTD run ace dataset again 
createLines(condition[1], "ace", "one") # 8018165
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/BCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/BCTD
sims[condition[1], "ace", "one"] <- 3 # output is on harddrive

# RCDD needs to go all over again
names(rcdd) <- c("8018262", "8018263", "8018264", "8018265", "8018267", "8018268")
transfer("one", "RCDD")

# SCDD need ace ptsd software virus again
# ace 8019246
# ptsd 8019247
# software 8019250
# virus 8019251
transfer("one", "SCDD")

# LCDD only ace 
createLines(condition[9], "ace", "one") # 8019423
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCDD/ace /Volumes/Gerbrich/asreview/simoutput/one/LCDD

# LCTD
# software 
createLines("LCTD", "software", "one") # 8020733
# scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCTD/software /Volumes/Gerbrich/asreview/simoutput/one/LCTD

# SCTD 
# ace ptsd software
sctd <- createLines("SCTD", c("ace", "ptsd", "software"), "one")
names(sctd) <- c("8025808", "8025809", "8025810")
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/SCTD
createLines("SCTD", "ptsd", "one") # 8066095
createLines("SCTD", "software", "one")
```

23.04.2020
Simulations for ace dataset again but now with seed. 
```{r, message = FALSE}
seed_ace <- createLines(condition[c(1, 2, 3,4,7,8,9)], "ace", "one", seed = TRUE) %>%
  noquote()
names(seed_ace) <- c(".", "8119459", "8119460", "8119461", "8119462", "8119463", "8119464")

seed_nudging <- createLines(condition[c(1, 2, 3,4,7,8,9)], "nudging", "one", seed = TRUE) %>%
  noquote()
names(seed_nudging) <- c("8119472", "8119472", "sctd", "")

# transfer sctd's later!(3)
noquote(transfer("one", condition[c(1, 2,4,7,8,9)], seed = TRUE))
# ace: scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one_seed/SCTD

@@
